Initial Analysis

### 2019-09-09 Initial_Analysis.Rmd
small updates
Include catches in main function

  }else{
  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbours_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Name)

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
# #The File
fnam_world <- "SAUEEZ_July2015.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

@@

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  EEZ_Neighbour_List <- EstNeighbours(World_EEZs, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

@@

#### For testing 
# Spp <- #600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG

# For EEZ
 # Neighbours <- Neighbours_EEZ
 # Index_Code <- EEZ_Index_Code

@@

# The function
EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type){

@@

@@

@@

@@

# __________________________________
# Test function
# __________________________________
# EstTransIndex(Spp = 600107,
#               Mode = "All",
#               Neighbours = ,Coord,Index_Code,Save="Y")
# 
# Spp <-  # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG
# 
# # For EEZ
#  # Neighbours <- Neighbours_EEZ
#  # Index_Code <- EEZ_Index_Code
#  
#  # For RFMO 
#  Index_Code <- RFMO_INDEX
#  Neighbours <- RFMO_Neighbor_List %>% 
#    rename(Territory = Name,
#          Neighbour = Neighbor_Territory)

@@

# Set Jurisdiction to EEZ or RFMO
Jurisdiction <- "RFMO"

@@

# Creates dummy dataset for Non transboundary species
write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)

@@

# Run model in parallel
system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List,
      FUN = EstTransIndex,
      Model = "All", # all data sources
      Neighbours = Neighbours_Data,
      Coord = CoorG,  # Gabriels coordinate system for read species dist
      Index_Code = Index_Code, 
      Save = "Y",  # For saving
      Jurisdiction_Type = Jurisdiction # For saving in proper path
    )
  )
)

>>>>

  }else{
  # Merge them with SAU data
  suppressWarnings(
    # warning for characters in name, no problem
  DBEM_Neighbours_Data <- Result_table %>% 
     left_join(EEZIDs_List, 
              by = "Name") %>% # Asign EEZ id to each country
    left_join(EEZ_CellID, 
              by = "EEZID") %>% # Asign EEZ id to each country
    left_join(Coor,
              by = "INDEX") %>%  # Inclu
    rename(Country_Territory = Territory)

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
# #The File
fnam_world <- "SAUEEZ_July2015.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

@@

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  EEZ_Neighbour_List <- EstNeighbours(World_EEZs, Partial = F)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

# user  system elapsed 
# 291.53  238.73  530.73 (SO MUCH FASTER!)

@@

#### For testing 
#Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
#Model <- "All"
#Coord = CoorG

# For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code

@@

# The function
EstTransIndex <- function(Spp,Model,Neighbours,Coord,Index_Code,Save="Y",Jurisdiction_Type,Catch = "N"){

@@

    File_Name <- paste(Spp,"_Transboundary.csv",sep = "")
    Save_Path <- paste(Results_Path,"/Trans_Results/",File_Name,sep="")

@@

    # Reads dataset of Non transboundary species
    Non_Transboundary_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep=""))

@@

    # Set a name for file and saves data
    New_Non_Name <- paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")
    write.csv(New_Non, New_Non_Name, row.names = F)

  ### Get Specie's catch

Catch_Data <- SppDist %>%
  filter(INDEX %in% Neighbours$INDEX,# Filter data only located within EEZs
           Model == "SAU_C",
         Value > 0) %>%
  left_join(Index_Code,
            by ="INDEX") %>% 
  group_by(TaxonKey,Territory) %>% 
  summarise(Total_Catch = sum(Value,na.rm=T))

  ### Save Catch data

 if(nrow(Catch_Data) > 0 & Catch == "Y"){

    File_Name <- paste(Spp,"_Catch.csv",sep = "")
    Save_Path <- paste(Results_Path,"/Catch_Results/",File_Name,sep="")

    write.csv(Catch_Data,
              Save_Path,
              row.names = F)

@@

# __________________________________
# Test function
# __________________________________
# EstTransIndex(Spp = 600004,
 #              Mode = "All",
  #             Neighbours = Neighbours_Data,
   #            Coord = CoorG,
    #           Index_Code=Index_Code,
     #          Jurisdiction_Type = "EEZ",
      #         Save="Y",
       #        Catch = "Y")

# Spp <-  # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG
# 
# # For EEZ
#  # Neighbours <- Neighbours_EEZ
#  # Index_Code <- EEZ_Index_Code
#  
#  # For RFMO 
#  Index_Code <- RFMO_INDEX
#  Neighbours <- RFMO_Neighbor_List %>% 
#    rename(Territory = Name,
#          Neighbour = Neighbor_Territory)

@@

@@

# Creates dummy dataset for Non transboundary species
write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Trans_Results/Non_Transboundary_Data.csv",sep=""), row.names = F)

@@

# Run model in parallel
system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List,
      FUN = EstTransIndex,
      Model = "All", # all data sources
      Neighbours = Neighbours_Data,
      Coord = CoorG,  # Gabriels coordinate system for read species dist
      Index_Code = Index_Code, 
      Save = "Y",  # For saving
      Catch = "Y",
      Jurisdiction_Type = Jurisdiction # For saving in proper path
    )
  )
)
